Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-02-01 Paper.tex
\hypertarget{Phi}{}
\hypertarget{Pi}{}

\hypertarget{Phi}{Phi}And finally define $\Phi$, the block transition function, which maps an incomplete block $B$ to a complete block $B'$:
\begin{eqnarray}
\Phi(B) & \equiv & B': \quad B' = B^* \quad \text{except:} \\
B'_n & = & n: \quad x \leqslant \frac{2^{256}}{H_d} \\
B'_m & = & m \quad \text{with } (x, m) = \mathtt{PoW}(B^*_{\hcancel{n}}, n, \mathbf{d}) \\
B^* & \equiv & B \quad \text{except:} \quad B^*_r = r(\Pi(\Gamma(B), B))
\end{eqnarray}
With $\mathbf{d}$ being a dataset as specified in appendix \ref{app:ethash}.

@@

\hypertarget{Pi}{Pi}Finally, we define $\Pi$ as the new state given the block reward function $\Omega$ applied to the final transaction's resultant state, $\ell(\boldsymbol{\sigma})$:
\begin{equation}
\Pi(\boldsymbol{\sigma}, B) \equiv \Omega(B, \ell(\boldsymbol{\sigma}))
\end{equation}

>>>>

\hypertarget{Phi}{}And finally define $\Phi$, the block transition function, which maps an incomplete block $B$ to a complete block $B'$:
\begin{eqnarray}
\Phi(B) & \equiv & B': \quad B' = B^* \quad \text{except:} \\
B'_n & = & n: \quad x \leqslant \frac{2^{256}}{H_d} \\
B'_m & = & m \quad \text{with } (x, m) = \mathtt{PoW}(B^*_{\hcancel{n}}, n, \mathbf{d}) \\
B^* & \equiv & B \quad \text{except:} \quad B^*_r = r(\Pi(\Gamma(B), B))
\end{eqnarray}
With $\mathbf{d}$ being a dataset as specified in appendix \ref{app:ethash}.

@@

\hypertarget{Pi}{}Finally, we define $\Pi$ as the new state given the block reward function $\Omega$ applied to the final transaction's resultant state, $\ell(\boldsymbol{\sigma})$:
\begin{equation}
\Pi(\boldsymbol{\sigma}, B) \equiv \Omega(B, \ell(\boldsymbol{\sigma}))
\end{equation}
